### 2024-09-30 paper-reviews/papers-2024.tex
Add MQA paper

    The paper examines how linguistic regularities are present in vector-space word representations implicitly learned by language models. The words are represented as high dimensional real valued vectors. The study shows that syntactic and semantic language regularities (male/female, singular/plural, etc.) are characterized by a relation-specific vector offset. The authors showed that it is possible to use the regularities to answers analogy questions.
\end{itemize}

>>>>

    The paper examines how linguistic regularities are present in vector-space word representations implicitly learned by language models. The words are represented as high dimensional real valued vectors. The study shows that syntactic and semantic language regularities (male/female, singular/plural, etc.) are characterized by a relation-specific vector offset. The authors showed that it is possible to use the regularities to answers analogy questions.

    \item \cite{Shazeer:MQA:2019}:

    The paper introduces multi-query attention (MQA) transformer architecture. Multi-query attention is identical to multi-head attention except that different heads share the same set of keys and values. The idea behind this change to transformer architecture is to improve memory to computation ratio. The authors show that execution performance gain are noticeable while model quality remains about the same.
\end{itemize}
